---
title: "Lab 01 - Hello R"
author: "Olivia Zhang"
date: "1/22/2025"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 variables in the datasaurus_dozen file. There variables included are dataset, which indicates which dataset the data are from, x values, and y values. 

```{r frequency table of the dataset variable}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

### Exercise 2

Here are the steps to look at the dino dataset.

First, the data in the dino dataset is plotted:

```{r plot-dino, fig.height=3, fig.width=6}
#filter out the dino dataset from datasaurus_dozen and name it as dino_data
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

#plot the data, with x on x axis, y on y axis, and each observation represented as points
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

As you can see, the plot of the dino dataset looks like a dinasour! What a surprise!

Next, the correlation between `x` and `y` in this dataset is calculated:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Although we can eye from the plot that x and y in the dino dataset does not have a linear relationship,
the correlation coefficient further comfirmed our observation: r = -.0645, which means x and y are 
barely correlated. 

### Exercise 3

Here are the steps to take a look at the star dateset:

First, the data in the star dataset is plotted:

```{r plot-star}
#filter out the star dataset from datasaurus_dozen and name it as star_data
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

#plot the data, with x on x axis, y on y axis, and each observation represented as points
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Wow, the plot of the star dataset looks like a star!

Next, the correlation between `x` and `y` in this dataset is calculated:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
Again, from the plot, we can tell that x and y in the star dataset does not have a linear relationship,
and the correlation coefficient comfirmed that x and y are barely correlated (r = -.063). 


### Exercise 4

Here are the steps to take a look at the circle dateset:

First, the data in the circle dataset is plotted:

```{r plot-circle}
#filter out the circle dataset from datasaurus_dozen and name it as circle_data
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

#plot the data, with x on x axis, y on y axis, and each observation represented as points
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Wow, the plot of the circle dataset looks like a circle!

Next, the correlation between `x` and `y` in this dataset is calculated:

```{r cor-circle}
star_data %>%
  summarize(r = cor(x, y))
```
Again, from the plot, we can tell that x and y in the circle dataset does not have a linear relationship,
and the correlation coefficient comfirmed that x and y are barely correlated (r = -.063). 

### Exercise 5

Now, I wonder, do all datasets look like their names? Let's plot them.

```{r plot-everything}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

They do! Since none of these datasets shows a linear relationship, 
are the correlation coefficients all close to zero?
```{r cor-everything}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
Wow, indeed! Amazing!
