---
title: "Lab 01 - Hello R"
author: "Olivia Zhang"
date: "1/22/2025"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 variables in the datasaurus_dozen file. There variables included are dataset, which indicates which dataset the data are from, x values, and y values. 

```{frequency table of the dataset variable}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

### Exercise 2

Here are the steps to look at the dino dataset.

First, the data in the dino dataset is plotted:

```{r plot-dino, fig.height=3, fig.width=6}
#filter out the dino dataset from datasaurus_dozen and name it as dino_data
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

#plot the data, with x on x axis, y on y axis, and each observation represented as points
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

As you can see, the plot of the dino dataset looks like a dinasour! What a surprise!

Next, the correlation between `x` and `y` in this dataset is calculated:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Although we can eye from the plot that x and y in the dino dataset does not have a linear relationship,
the correlation coefficient further comfirmed our observation: r = -.0645, which means x and y are 
barely correlated. 

### Exercise 3

Here are the steps to take a look at the star dateset:

First, the data in the star dataset is plotted:

```{r plot-star}
#filter out the star dataset from datasaurus_dozen and name it as star_data
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

#plot the data, with x on x axis, y on y axis, and each observation represented as points
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Wow, the plot of the star dataset looks like a star!

Next, the correlation between `x` and `y` in this dataset is calculated:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
Again, from the plot, we can tell that x and y in the star dataset does not have a linear relationship,
and the correlation coefficient comfirmed that x and y are barely correlated (r = -.063). 


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}

```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


