---
title: "Lab 01 - Hello R"
author: "Olivia Zhang"
date: "1/22/2025"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 variables in the datasaurus_dozen file. There variables included are dataset, which indicates which dataset the data are from, x values, and y values. 

```{frequency table of the dataset variable}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

### Exercise 2

First, the data in the dino dataset is plotted:

```{r plot-dino, fig.height=3, fig.width=6}
#filter out the dino dataset from datasaurus_dozen and name it as dino_data
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

#plot the data, with x on x axis, y on y axis, and each observation represented as points
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

As you can see, the plot of the dino dataset looks like a dinasour! What a surprise!

Next, the correlation between `x` and `y` in this dataset is calculated:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Although we can eye from the plot that x and y in the dino dataset does not have a linear relationship,
the correlation coefficient further comfirmed our observation: r = -.0645, which means x and y are 
barely correlated. 

### Exercise 3

This is your turn to write the code and narrative for the star dataset. Follow the same steps as above to complete the analysis. Don't forget to label your chunks appropriately!

Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.

```{r plot-star}
print("hello world!")
```

I'm some filler text, you should replace me with more meaningful text...

```{r cor-star}

```
Add your explanation here—what did you notice?


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}

```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


